Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
minor updates

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
\end{definition}

@@

\begin{proposition}
\label{prop:numberOfDistinguishedArrows}
Let~$F$ be a facet of~$\NKC$.
\begin{itemize}
 \item Each bending walk of~$F$ has exactly two distinguished arrows.
 \item Each finite straight walk of~$F$ has exactly one distinguished arrows.
 \item Each infinite straight walk of~$F$ has exactly zero distinguished arrows.
\end{itemize}
\end{proposition}
\begin{proof}
 \pierreguy{Vincent has the proof of this proposition.}
\end{proof}

>>>>

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i^{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
\end{definition}

@@

\begin{proposition}
\label{prop:numberOfDistinguishedArrows}
Let~$F$ be a facet of~$\NKC$.
\begin{itemize}
 \item Each bending walk of~$F$ has exactly two distinguished arrows.
 \item Each finite straight walk of~$F$ has exactly one distinguished arrows.
 \item Each infinite straight walk of~$F$ has exactly zero distinguished arrows.
\end{itemize}
\end{proposition}
\begin{proof}
 \pierreguy{Vincent has the proof of this proposition.}
 The first two dots in this proposition are proven in Lemma~\ref{lem:ExistenceOfDistinguishedArrows}.
\end{proof}
